---
title: "맞춤형 의학연구 애플리케이션을 위한 개발 환경 구축"
author: "Jinseob Kim"
date: "October 26, 2018"
output:
  slidy_presentation:
    highlight: pygments
    font_adjustment: +2
    duration: 40
    footer: "Copyright 2018, Jinseob Kim"
    fig_width: 7
    fig_height: 6
    fig_caption: true
    df_print: paged

---
 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```




# 예시 

## OK {.bigger}

$$1+1=2$$

---

asdasd

## Executive Summary 


맞춤형 의학연구 애플리케이션을 위해


1. **스웜 클러스터링** 환경에서 `Rstudio` & `Shiny-server` 를 구축하고


2. 의학 연구용 `ShinyApps` 를 만들었습니다.


# 시작

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure, fig.cap="A scatterplot."}
plot(pressure)
```

## datatable
```{r}
library(data.table);library(DT)
datatable(mtcars)
```



## df-paged
```{r}
mtcars
```